---
title: 'Final Project: Stardew Valley Fish Analysis'
author: "Christina Sauro"
date: "2023-04-05"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(magrittr)
library(tidyverse)
library(stringr)
library(forcats)
library(lubridate)
library(readr)
library(ggplot2)
set.seed(34)
```
# Introduction  

Stardew Valley is a popular farming simulator video game that is available on Steam. The game revolves around the user inheriting their grandfather's farm in an area called Pelican Town. There are several gameplay possibilities in the simulator, including cooking, foraging, crafting, fishing, farming, interacting with villagers of the town, and more.  

The game is built on a basic economic system with a currency of Gold. Players are motivated to earn Gold to develop their farm and purchase things for themselves. A large part of the game's economy is its fishing minigame. The player can catch different types of fish with different rarities and uses for their progress in the game. This project will be an analysis of the various types of fish in Stardew Valley and focus on the following questions:

1. Do fish sell higher or lower depending on type (basic, legendary, night market, catchable)?
- Even though it's pretty evident that basic fish will not be selling the highest, it might be useful to the player to see what category of fish sells for more money, as they can focus on type of fish to catch. I would predict that legendary fish would sell for the most, as they are normally found in rare places and at specific times. 

2. What are most fish used for (e.g. bundles, food, collectibles, etc.)?
- Each player can have different purposes for fishing in the game depending on their needs, so a player might focus on different fish depending on their use. I think that my results will show that most fish in the game will be used for finishing bundles, since they allow the player to advance the most in the game and unlock more items.

3. Where are most fish located among the game map?
- Depending where the user decides to fish, they can maximize the variety of fish they catch. I predict that most fish will be found in the main ocean of the town, as it's the most common area and one of the first places they are exposed to in the game. 

This fish catalog data from Kaggle and can be found [**here**](https://www.kaggle.com/datasets/jessicaebrown/stardew-valley-full-catelog). The villagers.csv file will not be included in this analysis.


# Data Wrangling Plan
I will be cleaning the seven files separately.

# Iteration 1 - fish_detail.csv
# Phase 1 
1. Read in the CSV file 
2. Change category names to lowercase 
3. Check if the data is in tidy format, pivot if the data is not
4. Idenfity uid's 
5. Sort by uid's 

# Phase 2  
```{r,echo=TRUE, eval=TRUE}
## 1 and 2
fish_detail <- read_csv("fish_detail.csv", col_types="??????????") %>% 
  rename_with(tolower) 

fish_detail %>% head(5)
```

3. I believe this data is tidy as a unique observation for each fish is noted in each row.   

The uid in this set would be the name of the fish, as it is the identifier of the observations in each row. To check this, I can use the following code chunk:
```{r,echo=TRUE, eval=TRUE}
## 4
fish_detail %>%
  count(name, location, season, weather) %>%
  filter(n > 1) %>%
  dim_desc()
```
I confirmed that the fish name is the uid.  

```{r, echo=TRUE, eval=TRUE}
## 5
fish_detail %<>%
  arrange(name) 
```

# Iteration 2- fish_detail.csv  
# Phase 1 
1. Convert character columns to lowercase 
2. Separate the difficulty & behaviour column 
3. Add new generalized columns
- Add new column for location, use, and type
4. Convert any character columns to factors  

# Phase 2  
```{r, echo=TRUE, eval=TRUE}
## 1

fish_detail %<>%
  mutate(across(c("name", "description", "location", "season", "used in", "weather"), tolower))
```

```{r, echo=TRUE, eval=TRUE}
## 2
fish_detail %<>%
  separate("difficulty & behavior", c("difficulty", "behaviour"), sep = " ", convert=TRUE)
```

For the location and usage columns, I used str_detect to check for seventeen common locations and five usages I noticed when looking through the data. 

```{r, echo=TRUE, eval=TRUE}
## 3
fish_detail %<>%
  mutate( located = case_when(
    location %>% str_detect("ginger island") ~ "ginger island",
    location %>% str_detect("mines") ~ "mines",
    location %>% str_detect("mountain lake") ~ "mountain lake",
    location %>% str_detect("river") ~ "river",
    location %>% str_detect("ocean") ~ "ocean",
    location %>% str_detect("witch's swamp") ~ "witch's swamp",
    location %>% str_detect("forest ") ~ "forest",
    location %>% str_detect("secret woods") ~ "secret woods",
    location %>% str_detect("mutant bug lair") ~ "mutant bug lair",
    location %>% str_detect("desert") ~ "desert",
    location %>% str_detect("volcano caldera") ~ "volcano caldera",
    location %>% str_detect("the sewers") ~ "the sewers",
    location %>% str_detect("jojamart") ~ "jojamart",
    location %>% str_detect("night market") ~ "night market",
    location %>% str_detect("freshwater") ~ "freshwater",
    location %>% str_detect("beach") ~ "beach",
    location %>% str_detect("any") ~ "any"
  )
  ) %>%
  select(name, location, located, everything())
```
I used the same method to create a new "usage" column. To check if a fish is being used for a food recipe, I created a vector of fish dishes from the game and used str_detect() to see if the fields matched any of the entries. The collected fish recipes are from the [**Stardew Valley Wiki**](https://stardewvalleywiki.com/Cooking) and can be found at the connected link.

```{r, echo=TRUE, eval=TRUE}
fish_recipes <- c("baked fish", "fried calamari", "lucky lunch", "carp surprise", "salmon dinner", 
                  "fish taco", "crispy bass", "tom kha soup", "trout soup", "fried eel", "spicy eel", 
                  "sashimi", "maki roll", "dish o' the sea", "seafoam pudding", "algae soup", 
                  "pale broth", "chowder", "fish stew", "lobster bisque", "crab cakes", 
                  "shrimp cocktail")

fish_detail %<>%
  mutate( 
    usage = (
      case_when(
        `used in` %>% str_detect("quest") ~ "quest",
        `used in` %>% str_detect("(loved gift)") ~ "gifts for villagers",
        `used in` %>% str_detect("bundle") ~ "bundle",
        `used in` %>% str_detect("no uses") ~ "no uses",
        `used in` %>% str_detect(str_c(fish_recipes, collapse = "|")) ~ "food",
      )
    )
  ) %>%
  glimpse()
```

```{r, echo=TRUE, eval=TRUE}
fish_detail %<>%
  mutate(
    type = "basic"
  )

fish_detail %<>% select(!c(location, `used in`)) # Dropping the columns that were used for recoding
```

```{r, echo=TRUE, eval=TRUE}
## 4
fish_detail %<>%
  mutate(across(!c("difficulty", "base xp"), as.factor))
```

# Iteration 1 - fish_price_breakdown.csv
# Phase 1
1. Read in the CSV file 
2. Change category names to lowercase 
3. Check if the data is in tidy format, pivot if the data is not
4. Idenfity uid's 
5. Sort by uid's

# Phase 2
```{r, echo=TRUE, eval=TRUE}
## 1 and 2
fish_breakdown <- read_csv("fish_price_breakdown.csv", col_types=paste(rep("c", 48), collapse=""))

fish_breakdown %<>% 
  rename_with(tolower)

fish_breakdown %>% head(5)
```

3. This data is not tidy and will need to be pivoted. Fish can be uniquely identified by their names, so I will pivot based on that category.
```{r, echo=TRUE, eval=TRUE}
## 3
fish_breakdown %<>%
  pivot_longer(!c("name"), names_to = "fish name", values_to = "price")
```

```{r, echo=TRUE, eval=TRUE}
## 4 - checking that fish name is the uid
fish_breakdown %>%
  count(`fish name`, name, price) %>%
  filter(n > 1) %>%
  dim_desc()

```
I've confirmed that the data is tidy and fish name is the uid.
```{r, echo=TRUE, eval=TRUE}
## 5
fish_breakdown %<>%
  select(`fish name`, everything())
fish_breakdown %<>%
  arrange(`fish name`)

```

# Iteration 2- fish_price_breakdown.csv  
# Phase 1
1. Convert character columns to lowercase 
2. Create classification column
3. Recode name column & rename it to rank
- The prefixes "bp", "fp", and "ap" will need to be removed.
4. Recode rank column
- Iridium was incorrectly spelled as irridium and needs to be changed
5. Recode price column
- Each entry has a "g" at the end of the value, meaning the gold currency. This should be removed to plot this column easier. 
6. Convert price column to a numeric column 
7. Convert any character columns to factors 
8. After cleaning the other tibbles, join the data into one tibble
- Pivot all tibbles wider
- Join regular fish and legendary fish tibbles together separately
- Add rows of each pivoted tibble based on fish name

# Phase 2
```{r, echo=TRUE, eval=TRUE}
## 1
fish_breakdown %<>%
  mutate(name = tolower(name))
```

Similar to how I checked the location column in the fish_detail data wrangling plan, I used a similar method to check the classification of the fish. Depending on the job of the player (no job, fisher, angler), some fish can sell for more Gold. 
```{r, echo=TRUE, eval=TRUE}
## 2
fish_breakdown %<>% 
  mutate(
    classification = (
      case_when(
        name %>% str_detect("bp|base price") ~ "base price",
        name %>% str_detect("fp|fisher profession") ~ "fisher profession",
        name %>% str_detect("ap|angler profession") ~ "angler profession"
      )
    )
  ) %>%
  select(name, classification, everything()) 

fish_breakdown %>% head(5)
```


```{r, echo=TRUE, eval=TRUE}
## 3
fish_breakdown %<>%
  mutate(name = str_remove_all(name, "bp |fp |ap "))

fish_breakdown %<>%
  mutate(name = case_when(
    str_detect(name, "base price|fisher profession|angler profession") ~ "regular",
    TRUE ~ name
          )
           )

fish_breakdown %<>%
  rename(rank = name)

fish_breakdown %<>% # renaming `fish name` to name to make future joining easier
  rename(name = `fish name`)
```

```{r, echo=TRUE, eval=TRUE}
## 4
fish_breakdown %<>%
  mutate(rank = str_replace_all(rank, "irridium", "iridium"))
```

```{r, echo=TRUE, eval=TRUE}
## 5
fish_breakdown %<>%
  mutate(price =  price %>% str_remove_all("g|,"))

fish_breakdown %>% head(5) #checking that all the recoding worked
```

```{r, echo=TRUE, eval=TRUE}
## 6
fish_breakdown %<>%
  mutate(price = as.numeric(price))

fish_breakdown %<>%
  select(name, everything())
```

```{r, echo=TRUE, eval=TRUE}
## 7
fish_breakdown %<>%
  mutate(across(name:classification, as.factor))
```

**I used the same process in the data wrangling plans to clean the rest of the files to be joined:**  
- legendary_fish_detail.csv  
- legendary_fish_price_breakdown.csv  
- legendaryfishII.csv  
- nightmarketfish.csv  
- crabpotandothercatchables.csv  

```{r, echo=FALSE, eval=TRUE}
## legendary_fish_detail.csv DWP P1
legendary_fish_detail <- read_csv("legendary_fish_detail.csv", col_types = "?????????") %>%
  rename_with(tolower)

legendary_fish_detail %<>%
  arrange(name)

## legendary_fish_detail.csv DWP P2
legendary_fish_detail %<>%
  mutate(across(!c("base xp"), tolower))

legendary_fish_detail %<>%
  separate("difficulty & behavior", c("difficulty", "behaviour"), sep = " ", convert=TRUE)

legendary_fish_detail %<>%
  mutate( located = case_when(
    location %>% str_detect("ginger island") ~ "ginger island",
    location %>% str_detect("mines") ~ "mines",
    location %>% str_detect("mountain lake") ~ "mountain lake",
    location %>% str_detect("river") ~ "river",
    location %>% str_detect("ocean") ~ "ocean",
    location %>% str_detect("witch's swamp") ~ "witch's swamp",
    location %>% str_detect("forest") ~ "forest",
    location %>% str_detect("secret woods") ~ "secret woods",
    location %>% str_detect("mutant bug lair") ~ "mutant bug lair",
    location %>% str_detect("desert") ~ "desert",
    location %>% str_detect("volcano caldera") ~ "volcano caldera",
    location %>% str_detect("the sewers") ~ "the sewers",
    location %>% str_detect("jojamart") ~ "jojamart",
    location %>% str_detect("night market") ~ "night market",
    location %>% str_detect("freshwater") ~ "freshwater",
    location %>% str_detect("beach") ~ "beach",
    location %>% str_detect("everywhere") ~ "any"
  )) %>%
  select(name, located, everything())

legendary_fish_detail %<>%
  mutate( 
    usage = "no uses"
     
  )

legendary_fish_detail %<>%
  mutate(
    type = "legendary"
  
  )

legendary_fish_detail %<>%
  mutate(across(!c("difficulty", "base xp"), as.factor ))
```

```{r, echo=FALSE, eval=TRUE}
#legendary_fish_breakdown.csv DWP
legendary_fish_breakdown <- read_csv("legendary_fish_price_breakdown.csv", col_types = "??????")

legendary_fish_breakdown %<>%
  rename_with(tolower)

legendary_fish_breakdown %<>%
  pivot_longer(!c("name"), names_to = "fish name", values_to = "price")

legendary_fish_breakdown %<>%
  select(`fish name`, everything())

legendary_fish_breakdown %<>%
  arrange(`fish name`)

legendary_fish_breakdown %<>%
  mutate(name = tolower(name))

legendary_fish_breakdown %<>%
  mutate(
    classification = (
      case_when(
        name %>% str_detect("bp|base price") ~ "base price",
        name %>% str_detect("fp|fisher profession") ~ "fisher profession",
        name %>% str_detect("ap|angler profession") ~ "angler profession"
      )
      
    )
    
    
  ) %>%
  select(name, classification, everything())

legendary_fish_breakdown %<>%
  mutate(name = str_remove_all(name, "bp |fp |ap "))


legendary_fish_breakdown %<>%
  mutate(name = case_when(
    str_detect(name, "base price|fisher profession|angler profession") ~ "regular",
    TRUE ~ name
    
  ))

legendary_fish_breakdown %<>%
  rename(rank = name)

legendary_fish_breakdown %<>%
  mutate(rank = str_replace_all(rank, "irridium", "iridium"))

legendary_fish_breakdown %<>%
  rename(name = `fish name`)

legendary_fish_breakdown %<>%
  mutate(price = price %>% str_remove_all("g|,"))

legendary_fish_breakdown %<>%
  mutate(price = as.numeric(price))

legendary_fish_breakdown %<>%
  select(name, everything())

legendary_fish_breakdown %<>%
  mutate(across(name:classification, as.factor))

```

```{r, echo=FALSE, eval=TRUE}
# legendaryfishii.csv DWP
legendary_fish_ii <- read_csv("legendaryfishII.csv", col_types=paste(rep("c", 12), collapse=""))

legendary_fish_ii %<>%
  rename_with(tolower)

legendary_fish_ii %<>%
  arrange(name)

legendary_fish_ii %<>%
  mutate(across(!c("base xp"), tolower))

legendary_fish_ii %<>%
  mutate(across(c("base xp"), as.numeric))

legendary_fish_ii %<>%
  separate("difficulty & behavior", c("difficulty", "behaviour"), sep = " ", convert=TRUE)

legendary_fish_ii %<>%
  mutate( located = case_when(
    location %>% str_detect("ginger island") ~ "ginger island",
    location %>% str_detect("mines") ~ "mines",
    location %>% str_detect("mountain lake") ~ "mountain lake",
    location %>% str_detect("river") ~ "river",
    location %>% str_detect("ocean") ~ "ocean",
    location %>% str_detect("witch's swamp") ~ "witch's swamp",
    location %>% str_detect("forest") ~ "forest",
    location %>% str_detect("secret woods") ~ "secret woods",
    location %>% str_detect("mutant bug lair") ~ "mutant bug lair",
    location %>% str_detect("desert") ~ "desert",
    location %>% str_detect("volcano caldera") ~ "volcano caldera",
    location %>% str_detect("the sewers") ~ "the sewers",
    location %>% str_detect("jojamart") ~ "jojamart",
    location %>% str_detect("night market") ~ "night market",
    location %>% str_detect("freshwater") ~ "freshwater",
    location %>% str_detect("beach") ~ "beach",
    location %>% str_detect("everywhere") ~ "any"
  )) %>%
  select(name, located, everything())

legendary_fish_ii %<>%
  mutate( 
    usage = "no uses"
  )

legendary_fish_ii %<>%
  mutate(
    type = "legendary"
  
  )

legendary_fish_ii %<>%
  separate("price", into=c("nr regular", "nr silver", "nr gold", "nr iridium"), sep ="[\\s]+", fill="right", convert=TRUE)

legendary_fish_ii %<>%
  separate("fisher profession (+25%)", into=c("fp regular", "fp silver", "fp gold", "fp iridium"), sep ="[\\s]+", fill="right", convert=TRUE)

legendary_fish_ii %<>%
  separate("angler profession (+50%)", into=c("ap regular", "ap silver", "ap gold", "ap iridium"), sep ="[\\s]+", fill="right", convert=TRUE)

legendary_fish_ii %<>%
  pivot_longer(cols = c(contains("nr"), contains("fp"), contains("ap")), names_to = "rank", values_to="price")

legendary_fish_ii %<>%
  mutate(
    classification = (
      case_when(
        rank %>% str_detect("nr") ~ "base price",
        rank %>% str_detect("fp") ~ "fisher profession",
        rank %>% str_detect("ap") ~ "angler profession"
      )
      
    )
    
    
  ) %>%
  select(name, rank, classification, everything())

legendary_fish_ii %<>%
  mutate(rank = str_remove_all(rank, "nr |fp |ap "))

legendary_fish_ii %<>%
  mutate(price = price %>% str_remove_all("g|,"))

legendary_fish_ii %<>%
  mutate(price = as.numeric(price))

legendary_fish_ii %<>%
  mutate(across(!c("difficulty", "base xp", "price"), as.factor ))

```

```{r, eval=TRUE, echo=FALSE}
# nightmarketfish.csv DWP
nightmarket_fish <- read_csv("nightmarketfish.csv", col_types=paste(rep("c", 9), collapse=""))

nightmarket_fish %<>%
  rename_with(tolower)

nightmarket_fish %<>%
  arrange(name)

nightmarket_fish %<>%
  mutate(across(!c("base xp"), tolower))

nightmarket_fish %<>%
  mutate(across(c("base xp"), as.numeric))

nightmarket_fish %<>%
  separate("difficulty & behavior", c("difficulty", "behaviour"), sep = " ", convert=TRUE)

nightmarket_fish %<>%
  mutate( located = "night market") %>%
  select(name, located, everything())

nightmarket_fish %<>%
  mutate(
    
    `used in` = replace_na(`used in`, "no uses")
    
  ) 

nightmarket_fish %<>%
  mutate( 
    usage = (
      case_when(
        `used in` %>% str_detect("quest") ~ "quest",
        `used in` %>% str_detect("(loved gift)") ~ "gifts for villagers",
        `used in` %>% str_detect("bundle") ~ "bundle",
        `used in` %>% str_detect("no uses") ~ "no uses",
        `used in` %>% str_detect(str_c(fish_recipes, collapse = "|")) ~ "food",
      )
    )
  ) 

nightmarket_fish %<>%
  mutate(
    type = "night market"
  
  )

nightmarket_fish %<>%
  separate("price", into=c("nr regular", "nr silver", "nr gold", "nr iridium"), sep ="[\\s]+", fill="right", convert=TRUE)

nightmarket_fish %<>%
  separate("fish profession (+25%)", into=c("fp regular", "fp silver", "fp gold", "fp iridium"), sep ="[\\s]+", fill="right", convert=TRUE)

nightmarket_fish %<>%
  separate("angler profession (+50%)", into=c("ap regular", "ap silver", "ap gold", "ap iridium"), sep ="[\\s]+", fill="right", convert=TRUE)

nightmarket_fish %<>%
  pivot_longer(cols = c(contains("nr"), contains("fp"), contains("ap")), names_to = "rank", values_to="price") 

nightmarket_fish %<>%
  mutate(
    classification = (
      case_when(
        rank %>% str_detect("nr") ~ "base price",
        rank %>% str_detect("fp") ~ "fisher profession",
        rank %>% str_detect("ap") ~ "angler profession"
      )
      
    )
    
    
  ) %>%
  select(name, rank, classification, everything())

nightmarket_fish %<>%
  mutate(rank = str_remove_all(rank, "nr |fp |ap "))

nightmarket_fish %<>%
  mutate(price = price %>% str_remove_all("g|,"))

nightmarket_fish %<>%
  mutate(price = as.numeric(price))

nightmarket_fish %<>%
  mutate(across(!c("difficulty", "base xp", "price"), as.factor ))
```

```{r, eval=TRUE, echo=FALSE}
#crabpotandothercatchables.csv DWP
crabpot_catchables <- read_csv("crabpotandothercatchables.csv", col_types=paste(rep("c", 10), collapse=""))

crabpot_catchables %<>%
  rename_with(tolower)

crabpot_catchables %<>%
  drop_na("name")
  
crabpot_catchables %<>%
  arrange(name)

crabpot_catchables %<>%
  mutate(name = str_remove_all(name, "\\[2\\]"),)

crabpot_catchables %<>%
  mutate(across(everything(), tolower))

crabpot_catchables %<>%
  rename(`trap chance (non-mariner)` = `trap chance`,
         `trap chance (mariner)` = ...8)

crabpot_catchables %<>%
  mutate( located = case_when(
    location %>% str_detect("ginger island") ~ "ginger island",
    location %>% str_detect("mines") ~ "mines",
    location %>% str_detect("mountain lake") ~ "mountain lake",
    location %>% str_detect("river") ~ "river",
    location %>% str_detect("ocean") ~ "ocean",
    location %>% str_detect("witch's swamp") ~ "witch's swamp",
    location %>% str_detect("forest") ~ "forest",
    location %>% str_detect("secret woods") ~ "secret woods",
    location %>% str_detect("mutant bug lair") ~ "mutant bug lair",
    location %>% str_detect("desert") ~ "desert",
    location %>% str_detect("volcano caldera") ~ "volcano caldera",
    location %>% str_detect("the sewers") ~ "the sewers",
    location %>% str_detect("jojamart") ~ "jojamart",
    location %>% str_detect("night market") ~ "night market",
    location %>% str_detect("freshwater") ~ "freshwater",
    location %>% str_detect("beach") ~ "beach",
    location %>% str_detect("everywhere") ~ "any"
  )) %>%
  select(name, located, everything())


crabpot_catchables %<>%
  mutate(
    
    `used in` = replace_na(`used in`, "no uses")
    
  ) 

fish_recipes <- c("baked fish", "fried calamari", "lucky lunch", "carp surprise", "salmon dinner", "fish taco", "crispy bass", "tom kha soup", "trout soup", "fried eel", "spicy eel", "sashimi", "maki roll", "dish o' the sea", "seafoam pudding", "algae soup", "pale broth", "chowder", "fish stew", "lobster bisque", "crab cakes", "shrimp cocktail")

crabpot_catchables %<>%
  mutate( 
    usage = (
      case_when(
        `used in` %>% str_detect("quest") ~ "quest",
        `used in` %>% str_detect("(loved gift)") ~ "gifts for villagers",
        `used in` %>% str_detect("bundle") ~ "bundle",
        `used in` %>% str_detect("no uses") ~ "no uses",
        `used in` %>% str_detect(str_c(fish_recipes, collapse = "|")) ~ "food",
      )
    )
  ) 


crabpot_catchables %<>%
  mutate(
    type = "crabpot/catchable"
  
  )

crabpot_catchables %<>%
  separate("price", into=c("nr regular", "nr silver", "nr gold", "nr iridium"), sep ="[\\s]+", fill="right", convert=TRUE)

crabpot_catchables %<>%
  separate("fisher profession (+25%)", into=c("fp regular", "fp silver", "fp gold", "fp iridium"), sep ="[\\s]+", fill="right", convert=TRUE)

crabpot_catchables %<>%
  separate("angler profession (+50%)", into=c("ap regular", "ap silver", "ap gold", "ap iridium"), sep ="[\\s]+", fill="right", convert=TRUE)

crabpot_catchables %<>%
  pivot_longer(cols = c(contains("nr "), contains("fp "), starts_with("ap ")), names_to = "rank", values_to="price") 

crabpot_catchables %<>%
  mutate(
    classification = (
      case_when(
        rank %>% str_detect("nr") ~ "base price",
        rank %>% str_detect("fp") ~ "fisher profession",
        rank %>% str_detect("ap") ~ "angler profession"
      )
      
    )
    
    
  ) %>%
  select(name, rank, classification, everything())

crabpot_catchables %<>%
  mutate(rank = str_remove_all(rank, "nr |fp |ap "))

crabpot_catchables %<>%
  mutate(price = price %>% str_remove_all("g|,"))

crabpot_catchables %<>%
  mutate(price = as.numeric(price))

crabpot_catchables %<>%
  mutate(rank = str_remove_all(rank, "%"),
         `trap chance (non-mariner)` = str_remove_all(`trap chance (non-mariner)`, "%"),
         `trap chance (mariner)` = str_remove_all(`trap chance (mariner)`, "%")
         )

crabpot_catchables %<>%
  mutate(price = price %>% str_remove_all("g|,"))

crabpot_catchables %<>%
  mutate(price = as.numeric(price),
         `trap chance (non-mariner)` = as.numeric(`trap chance (non-mariner)`),
         `trap chance (mariner)` = as.numeric(`trap chance (mariner)`))

crabpot_catchables %<>%
  select(!c("used in", "location", "trap chance (non-mariner)", "trap chance (mariner)"))

crabpot_catchables %<>%
  mutate(across(c("name", "rank", "classification", "description",  "size (inches)", "usage", "located", "type"), as.factor ))

```

```{r, echo=TRUE, eval=TRUE}
legendary_fish_detail %>%
  head(5)

legendary_fish_breakdown %>%
  head(5)

legendary_fish_ii %>%
  head(5)

nightmarket_fish %>%
  head(5)

crabpot_catchables %>%
  head(5)
```

```{r, eval=TRUE, echo=TRUE}
## 8 - pivotting the basic fish tibbles to be longer
fish_breakdown %<>%
  pivot_wider(names_from = "classification", values_from = "price")

fish_breakdown %<>%
  pivot_wider(names_from = "rank", values_from = c("base price", "fisher profession", 
                                                   "angler profession"), names_sep = " ")

```
I pivoted the other 5 files to be wider as well based on their classification.
```{r, echo=FALSE, eval=TRUE}
## 1. Pivoting the legendary_fish_detail, 
legendary_fish_ii %<>%
  pivot_wider(names_from = "classification", values_from = "price")

legendary_fish_ii %<>%
  pivot_wider(names_from = "rank", values_from = c("base price", "fisher profession", "angler profession"), names_sep = " ")

legendary_fish_breakdown %<>%
  pivot_wider(names_from = "classification", values_from="price")

legendary_fish_breakdown %<>% 
  pivot_wider(names_from = "rank", values_from = c("base price", "fisher profession", "angler profession"), names_sep = " ")

```

```{r, eval=TRUE, echo=FALSE}
## 1. Pivotting the nightmarket_fish tibble

nightmarket_fish %<>%
  pivot_wider(names_from = "classification", values_from = "price")

nightmarket_fish %<>%
  pivot_wider(names_from = "rank", values_from = c("base price", "fisher profession", "angler profession"), names_sep = " ")

```

```{r, eval=TRUE, echo=FALSE}
#1 Pivoting the crabpot_catchable tibble

crabpot_catchables %<>%
  pivot_wider(names_from = "classification", values_from = "price")

crabpot_catchables %<>%
  pivot_wider(names_from = "rank", values_from = c("base price", "fisher profession", "angler profession"), names_sep = " ")


```

```{r, eval=TRUE, echo=TRUE}
## 8 - joining the basic and legendary fish tibbles together separately

fish_tibble <- left_join(fish_detail, fish_breakdown, by = "name")

fish_tibble %>% # checking that left join worked
  head(5)

leg_fish_tibble <- left_join(legendary_fish_detail, legendary_fish_breakdown, by = "name")
leg_fish_tibble %<>%
  bind_rows(legendary_fish_ii)

leg_fish_tibble %>% # checking that left join and binding worked
  head(5)

```
The legendary_fish_ii tibble contained information related to the fish's details and price, so to join it properly with the other two tibbles, I needed to add the tibble's rows to leg_fish_tibble.  
Both tibbles include the new columns and rows, which confirms the left join and binding worked.

```{r, eval=TRUE, echo=TRUE}
## 8 - binding rows to one main tibble from data with different fish types

main_tibble <- fish_tibble %>%
  bind_rows(leg_fish_tibble, nightmarket_fish, crabpot_catchables)

main_tibble %>% # check that binding worked
  glimpse()
```
The main tibble has basic, legendary, night market, and crabpot/catchable names therefore the binding operation worked.

```{r, eval=TRUE, echo=TRUE}
## 8 - pivotting the main tibble to be longer so that it can be plotted correctly

main_tibble %<>%
  pivot_longer(cols = c(contains("profession"), contains("base price")), names_to = "rank",
               values_to="price") 

main_tibble %<>%
  mutate(across(c("located", "rank", "usage"), as.factor))
```
I can drop the "location" and "used in" column as I have already recoded these columns. I can also drop the "size" column as it's not relevant to the data and it's not recorded for the legendary, nightmarket, or crabpot data.

```{r, eval=TRUE, echo=TRUE}
main_tibble %<>%
  select(!c("location", "size", "used in"))

main_tibble %<>% # dropping rows with NA where prices were not recorded 
  drop_na(price)

```

# Results/Discussion
# Question 1: Do fish sell higher or lower depending on type?  
```{r, eval=TRUE, echo=TRUE}

p1 <- main_tibble %>%
  ggplot(aes(x = price, y = fct_reorder(str_to_title(type), price, .desc = TRUE),
             colour = fct_reorder(str_to_title(type), price, .desc = TRUE))) + 
  geom_boxplot(width = 0.7) + 
  labs(x = "Price of Fish", y = "Type of Fish") + 
  scale_x_continuous(trans = "log10", label = scales::label_number(suffix = "g"), n.breaks = 8) +
  guides(colour = "none") +
  ggtitle("Fish Type Against Price Correlation in Stardew Valley") + 
  scale_colour_viridis_d(option = "C") + 
  theme_minimal() +
  theme(
        plot.title = element_text(hjust = 0.5, size= 11),
        axis.title = element_text(size = 10))
```

```{r, eval=TRUE, echo=FALSE, fig.cap = "Fish Type Against Price Correlation in Stardew Valley", fig.width=5, fig.height=2.5}
p1
```  


Figure 1 indicates that legendary fish in Stardew Valley clearly sell the highest, and crabpot/other catchables sell lowest. This is expected, as most catchable items were more common plant items like Algae. Basic and legendary types have more possible outliers that sell for a higher price, which is surprising. There is a steady decrease in price from the highest to lowest column. The night market category has no possible outliers, which makes sense, as there was very little data recorded for this type. Basic fish have a wider range of price, which is also unsurprising as there were a lot of fish in this category compared to the others.  

# Question 2: What are most fish used for?  
```{r, eval=TRUE, echo=TRUE}
p2_tibble <- main_tibble %>% # Creating a new tibble counting the frequency of each location
  group_by(usage) %>%
  summarise(
    count = n()
  )

p2 <- p2_tibble %>%
  ggplot(aes(x = fct_reorder(str_to_title(usage), count, .desc = TRUE), y = count, 
             fill = fct_reorder(str_to_title(usage), count, .desc = TRUE))) + 
  geom_col(width = 0.5) + 
  guides(fill = "none") +
  labs(x = "Usage", y = "Count")+
  scale_y_continuous(n.breaks = 7) + 
  ggtitle("Density of Fish Usage in Stardew Valley") + 
  scale_fill_viridis_d(option = "C") + 
  theme_minimal() + 
  theme(
    plot.title = element_text(hjust = 0.5, size=12),
    axis.title = element_text(size=10)
  )
```
```{r, eval=TRUE, echo=FALSE, fig.cap = "Density of Fish Usage in Stardew Valley", fig.width=5, fig.height=2.5}
p2
``` 


Figure 2 indicates that most fish caught in the game are not used for any specific purpose. After the most frequent column, bundles are the second highest use for caught fish. This could potentially be because the game was designed to encourage players to complete bundles for advantages. There is a noticeable decrease for the three columns with the lowest frequency- food, gifts for villagers, and quests. Quests are the lowest category that fish are used for in the game.  

# Question 3: Does fish location correlate to selling price?
The same grouping process for Question 2 was done for the "located" column in the third plot.  
```{r, eval=TRUE, echo=FALSE}
p3_tibble <- main_tibble %>%
  group_by(located) %>%
  summarise(
    count = n()
  )
```

```{r, eval=TRUE, echo=TRUE}
p3 <- p3_tibble %>%
  ggplot(aes(y = fct_reorder(str_to_title(located), count, .desc = FALSE), x = count,
             fill = fct_reorder(located, count, .desc = FALSE))) +
  geom_col(width = 0.5) +
  guides(fill = "none") +
  labs(x = "Count", y = "Location") +
  scale_x_continuous(breaks = c(0, 25, 50, 75, 100, 125, 150, 175, 200)) +
  ggtitle("Density of Fish Location in Stardew Valley") +
  scale_fill_viridis_d(option = "C") +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size=12),
    axis.title = element_text(size=10)
  )
```
```{r, eval=TRUE, echo=FALSE, fig.cap = "Density of Fish Location in Stardew Valley", fig.width=5, fig.height=2.5}
p3
```

  
Figure 3 indicates that the highest location where fish are caught in Stardew Valley is the ocean.  This is expected as it is a larger area within the town. There is a lot of variation between the locations shown in the plot. The plot also suggests that Mountain Lake, River, and Ginger Island are quite close in frequency of fish location. Mutant Bug Lair, Freshwater, and Any (specifying the fish could be found in any location) were locations with the lowest frequency.

# Conclusion  
I was able to use the generated results to answer my previous questions at the start of the analysis:  

1. Do fish sell higher or lower depending on type?  
The boxplot created shows that fish type does seem to impact their selling price. Legendary and night market fish sell for higher, while basic and crabpot/catchable fish tend to sell for lower. There is a steady increase in price between the columns. A player might want to consider looking for legendary fish to catch if they were looking to make more Gold. The results of this plot match my hypothesis for this question.  
2. What are most fish used for?  
Results from the previous plot show that most fish in Stardew Valley are not used for any specific reason, and are mainly just collectibles. Furthermore, fish were used frequently for completing bundles, and were less frequently used to craft food, given to villagers, and used to complete quests. There was a distinct increase in frequency for the no uses and bundles category, while the food, gifts for villagers, and quest categories were similar in low frequency. The results of this plot do not support my hypothesis for this question, which was that the most frequent use of fish would be for completing bundles.  

3. Where are most fish located among the game map?  
The bar chart used for this question implies that most fish were located in the ocean. Fish that could be found in any location were the least frequent. Depending on where the player is on the map, they could focus on a specific location depending on this data to maximize the fish they catch. The results from this plot support my hypothesis for this question. 

The overall results of this analysis show that the player of Stardew Valley can gain both money and a high quantity of fish by focusing on fish type, usage, and location. Type and purpose of fish are clearly tailored to a specific purpose and location. In a game that thrives on economy and earning Gold, the player can use this data to their advantage when fishing in Stardew Valley. 

I believe this analysis could be improved if the data was recorded more consistently. Many columns needed to be recoded because of spelling errors or lack of information. In addition, potentially automating the recoding of columns might make the analysis cleaner and easier. For example, I needed to use 17 lines of code when recoding the location column for the fish_detail tibble. It would be very beneficial if there was an easier way to do this. 


# References
- [**Stardew Valley FULL Catalog on Kaggle**](https://www.kaggle.com/datasets/jessicaebrown/stardew-valley-full-catelog)  

- [**Cooking - Stardew Valley Wiki**](https://stardewvalleywiki.com/Cooking)
